---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# typed

<!-- badges: start -->
<!-- badges: end -->

The goal of typed is to provide wrappers that allow developers to create 'type-safe' functions. This _does not_ make functions typesafe, rather it returns a result that is checked at runtime and flagged as valid or not.

The main purpose of this package is for integration with typesafe APIs, such as TypeScript. Typed functions will (eventually) gain capabilities to generate TypeScript definitions that can be used, for example by rserve-js or similar.

## Installation

You can install the development version of typed like so:

```{r, eval=FALSE}
remotes::install_github('tmelliott/typed')
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r}
library(typed)

mean_double <- typed(mean,
    list(x = "number[]"),
    value = number()
)
mean_double
mean_double(1:5)

mean_char <- typed(mean, value = string())
mean_char
mean_char(1:5)
```

TypeScript definitions can be generated:

```{r}
compile(mean_double)
compile(mean_char)
```

## Advanced demo

Create array types using the `array_type()` function:

```{r}
random_numbers <- typed(runif,
    list(n = "number"),
    value = array_type(number())
)
random_numbers
random_numbers(10)
```

Create union types using the `union()` function:

```{r}
flip_coins <- function(n) ifelse(runif(n) > 0.5, "heads", "tails")
coin_tosses <- typed(flip_coins,
  value = array_type(union(litteral("heads"), litteral("tails")))
)
coin_tosses
coin_tosses(10)
```

Finally, complex object types can be defined using the `object()` function:

```{r}
person <- typed(
  function(name, age, employed, gender) {
    p <- list(name = name, age = age, employed = employed)
    if (!missing(gender))
      p$gender <- gender
    p
  },
  value = object(
    name = string(),
    age = number(),
    employed = boolean(),
    gender = union(
      litteral("male"),
      litteral("female"),
      litteral("other")
    ) |> optional()
  )
)
person
person("Joe", round(runif(1, 20, 50)), TRUE)
```

It might be easier to define types for later use, or extension.

```{r}
date_type <- object(
  year = number(),
  month = number(),
  day = number()
)
event_type <- object(
  name = string(),
  date = date_type,
  attendees = optional(array_type(string()))
)

get_events <- typed(
  function() {
    list(
      list(
        name = "Birthday",
        date = list(year = 2020, month = 1, day = 1),
        attendees = c("Joe", "Jane")
      ),
      list(
        name = "Christmas",
        date = list(year = 2020, month = 12, day = 25),
        attendees = c("Joe", "Jane", "Santa")
      )
    )
  },
  value = array_type(event_type)
)
get_events
get_events()
```
